Model Finding for (Co)recursive Functions in SMT\thanks{ This research is partially supported by the Inria technological development action \relax{Contrexemples Utilisables par Isabelle et Coq} (CUIC). }

### 2015-05-05 tex/main.tex
Minor

\begin{theorem}
If $\varphi$ be a $\Sigma$-formula that is well-defined with respect to functions $\sfundefs{\Sigma}$,
and the set of function definitions corresponding to functions in $\sfundefs{\Sigma}$ is well-specified,
then $\varphi$ and $\conv( \varphi )$ are equisatisfiable.
\end{theorem}
\begin{proof}
(Sketch)  First, we show that if $\varphi$ has a model $\I$, then $\conv( \varphi )$ has a model $\J$.
Let $\J$ be the $\extendsig{\Sigma}$-interpretation that interprets all sorts $\sigma \in \ssorts{\Sigma}$ as $\sigma^\I$,
all functions $f \in \sfuns{\Sigma}$ as $f^\I$,
and for each function $f$ of type $\tau_1 \times \ldots \tau_n \rightarrow \tau$ in $\sfundefs{\Sigma}$, 
interprets $\fargsort{f}$ as a tuple of values of type $\tau_1^\I \times \ldots \times \tau_n^\I$,
and each $\farg{f}^i$ as the $i^{th}$ projection on such tuples for each $i = 1, \ldots, n$.
Note that $\J$ satisfies \emph{every} constraint of the form $\exists z\typ{\fargsort{f}}. ( \vecfarg{f}( z ) \teq \vec t )$,
since by our construction of $\J$ there exists a $z$ such that $z^\J = \vec t^\J$.
By case analysis it follows that $\conv_0$ maintains the invariant that
if $\conv_0( t\typ{\Bool}, \ptrue )$ returns $( r\typ{\Bool}, D )$,
then $\I$ satisfies $t$ if and only if $\J$ satisfies $r$.
Thus, we conclude $\J$ is a model of $\conv( \varphi )$.

>>>>

\begin{theorem}
If $\varphi$ be a $\Sigma$-formula that is well-defined with respect to functions $\sfundefs{\Sigma}$,
and the set of function definitions corresponding to functions in $\sfundefs{\Sigma}$ is well-specified,
then $\varphi$ and $\conv( \varphi )$ are equisatisfiable.
\end{theorem}
\begin{proof}
(Sketch)  First, we show that if $\varphi$ has a model $\I$, then $\conv( \varphi )$ has a model $\J$.
Let $\J$ be the $\extendsig{\Sigma}$-interpretation that interprets all types $\tau \in \ssorts{\Sigma}$ as $\tau^\I$,
all functions $f \in \sfuns{\Sigma}$ as $f^\I$,
and for each function $f$ of type $\tau_1 \times \ldots \tau_n \rightarrow \tau$ in $\sfundefs{\Sigma}$, 
interprets $\fargsort{f}$ as a tuple of values of type $\tau_1^\I \times \ldots \times \tau_n^\I$,
and each $\farg{f}^i$ as the $i^{th}$ projection on such tuples for each $i = 1, \ldots, n$.
Note that $\J$ satisfies \emph{every} constraint of the form $\exists z\typ{\fargsort{f}}. ( \vecfarg{f}( z ) \teq \vec t )$,
since by our construction of $\J$ there exists a $z$ such that $z^\J = \vec t^\J$.
By case analysis it follows that $\conv_0$ maintains the invariant that
if $\conv_0( t\typ{\Bool}, \ptrue )$ returns $( r\typ{\Bool}, D )$,
then $\I$ satisfies $t$ if and only if $\J$ satisfies $r$.
Thus, we conclude $\J$ is a model of $\conv( \varphi )$.
